Active Contextual Entropy Search

### 2016-06-07 2016_ICML/poster/content/left_column.tex
Adding further illustrating examples

\begin{figure}
\centering
\includegraphics[width=0.48\columnwidth]{../pics/regret_illustration}
\includegraphics[width=0.48\columnwidth]{../pics/acq_comparison}
\caption{(Left) GP posterior, probability of maximum $p^\star$, expected regret ER, and  $\mathbb{E}[\max(f(\mathbf{x}) - f(1.5), 0)]$ (scale on right-hand side). (Right) GP posterior and different acquisition function. Absolute values have been normalized such that the mean value of acquisition function is $0.5$.}
\label{fig:MRS_illustration}
\end{figure}
\end{block}

>>>>

\begin{figure}
\centering
\includegraphics[width=0.48\columnwidth]{../pics/regret_illustration_2}
\includegraphics[width=0.48\columnwidth]{../pics/regret_scatter}
\caption{(Left) GP posterior, probability of maximum $p^\star$, and expected regret ER. (Right) Scatter plot of position of optimum and regret of $\mathbf{\tilde x} = 1.5$ versus optimum in sample functions.}
\label{fig:MRS_illustration}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=0.48\columnwidth]{../pics/acq_comparison}
\caption{GP posterior and different acquisition function. Absolute values have been normalized such that the mean value of acquisition function is $0.5$.}
\label{fig:MRS_illustration}
\end{figure}
\end{block}
